---
title: "BARS Package Test Output"
author: "Developed by Andy Shen"
output:
  pdf_document: default
---

# Introduction and Installation

Hello! Thank you for taking the time to test the `bars` package in R. This package lays out the foundation for Bayesian Adaptive Regression Splines, a common tool used to fit nonlinear data from a Bayesian perspective. This algorithm utilizes various MCMC techniques, such as Reversible-Jump algorithms and Gibbs sampling to adaptively predict the optimal number of knots and their locations without overfitting the data. I am still writing the Vignette and will upload it to the repository when it is completed.

Please run the code below and ensure all outputs appear exactly as the file `TEST_FILE.pdf` which can be found on the GitHub repository for this project: https://github.com/aashen12/BARS. In its entirety, the file should take around 1 minute to run completely, depending on your processor speed.

If you encounter any errors that you cannot fix after multiple attempts, please send me a screenshot of the full error message as well as the entire pdf/Rmd file with the error. You can email me (Andy) at aashen@ucla.edu. Please do not hesitate to email me if you have any questions as well.

Thanks again, and enjoy!

To install the `bars` package, please run the following command in your RStudio console:

```{r, eval=FALSE}
devtools::install_github("aashen12/BARS") # only run this command once
```


\pagebreak

# Your name here

# Data Generation

```{r setup, include=FALSE}
# Do not modify this code
# devtools::load_all()
# devtools::install()
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = TRUE)
```


```{r}
rm(list = ls())
set.seed(12) # feel free to modify once you get the code working
n <- 300
x <- seq(0,1,length.out=n)
y <- sin(2*pi*x^2)*10+rnorm(n)
plot(x, y)
```

Feel free to play around with the data and modify however you like once you get this code working.

\pagebreak

# Bayesian Spline with Random Knots

```{r}
library(bars) #crucial step in calling the package
library(mvtnorm) #this line is necessary...for now
nmcmc <- 5000
res <- bars(its = nmcmc, verbose = TRUE)
```

# Results

## Beta

```{r}
beta <- res$beta
beta <- beta[,colSums(is.na(beta)) != nrow(beta)]
round(beta[nrow(beta),], 2)
```

## Sigma

```{r}
sig <- res$sig
tail(round(sig, 2))
```

## Knots

```{r}
knots <- res$knots
knots <- knots[,colSums(is.na(knots)) != nrow(knots)] 
round(knots[nrow(knots),], 2)
res$knots_total
```

\pagebreak

## Signs

```{r}
signs <- res$signs
signs <- signs[,colSums(is.na(signs)) != nrow(signs)]
round(signs[nrow(signs),], 2)
```

# Basis Functions

```{r}
X <- res$X
tail(round(X, 2))
```

\pagebreak

# Plotting Predicted Values

```{r}
knotnum <- ncol(knots)
mean.pred <- matrix(NA, nrow = nmcmc, ncol = length(x))
pred <- mean.pred
for(p in 1:nmcmc) {
  splb <- spline.basis(nknot = knotnum, knots = knots[p,], signs = signs[p,])
  mean.pred[p,] <- splb %*% beta[p,]
  pred[p,] <- mean.pred[p,] + rnorm(length(x), sd = sqrt(sig[p])) 
}
mean.pred <- t(mean.pred)
```

```{r}
pred_adj <- t(apply(pred, 2, quantile, probs = c(0.025, 0.975), na.rm = TRUE))
matplot(x, pred_adj, col = "lightgrey", lwd = 5, type = "l")
matplot(x, mean.pred, type = "l", lwd = 9, add = TRUE)
points(x, y)
```

\pagebreak

# Plot of Averages

```{r}
plot(x, rowMeans(mean.pred, na.rm = TRUE), lwd = 8, type = "l", col = "royalblue")
points(x, y)
```

